---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  message = FALSE 
)
```

# hexbur

<!-- badges: start -->
<!-- badges: end -->

The goal of hexbur is to provides several layers of information for Burkina Faso, useful for agricultural systems analysis and more.

## Installation

You can install the development version of hexbur from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("oousmane/hexbur")
```

## Example

The package is based on a hexagonal grid of Burkina Faso, to which data layers can be added. This grid may be loaded as follows,
using the `hex_map()` function
```{r example}
library(hexbur)
hex <- hex_map() # with no args.

```

A very quick viz of hex grids can be performed using `{sf}` and for sure the `{tidyverse}`

```{r cars}
#| warning
library(hexbur)
library(sf)
library(tidyverse)

hex <- hex_map() # with no args.

# Simple hex grid map 
ggplot()+
  geom_sf(data = hex)
```

